### 2018-10-16 Latex/section_methods.tex
Article compiled with a Makefile (without figure).
Start to include figures in the pdf file.
Rename and improve figures
Change width in Latex to equivalent in inches
First revision by Erik

\subsection{Numerics}

From a numerical point of view, it is convenient to solve for the
eigenmodes of the linear operator $\hat q$ and $\hat a_\pm = \hat a
/2 \pm \omega_l \hat d /(2i)$.
%
We thus consider the following modified governing equations
\begin{eqnarray}
\bigl( \p_t  + \fdiss(\kk) \bigl) \hat q  
&=& \hat N_q  ,\label{eqqnum} \\
\bigl( \p_t  + \fdiss(\kk) \pm  i \omega_l \bigl)  \hat a_\pm  
&=& \hat N_{\pm} + \hat f_{\pm}, \label{eqapmnum}
\end{eqnarray}
where $\hat f_{\pm}$ are forcing terms and %
$\hat N_q$ and %
$\hat N_\pm = \hat N_a /2 \pm \omega_l \hat N_d/(2i)$ %
are non-linear terms computed from %
$\hat \NN_\uu = - \zeta \eez \wedge \uu - \bnabla |\uu|^2/2$ and %
$\hat N_\eta = - \bnabla \cdot (\eta \uu)$.
%
We have removed the Newtonian viscous operator in (\ref{eq_uu}) and
added more general dissipative operators in (\ref{eq_uu}) and
(\ref{eq_h}).  There is no strong physical motivations for this
modification but, as discussed by \cite{FargeSadourny1989}, molecular
dissipation of the form $\nu \bnabla^2 \uu$ is not necessarily a
relevant model of the actual small-scale dissipation for shallow-water
flows, which should rather be described as a transition from
two-dimensional to three-dimensional motions before reaching the
scales where dissipation actually occurs.

Equations (\ref{eqqnum}-\ref{eqapmnum}) are simulated by means of a
pseudo-spectral method with periodic boundary conditions.
%
Time advancement is carried out by a classical fourth-order
Runge-Kutta scheme for the nonlinear term and an exact integration for
the linear and dissipative terms.  This explicit integration is
especially interesting at very high resolution and very large $c$ when
the shortest waves are very fast with frequency of the order of
$\omega \simeq c \max(k)$.
%
We use an adaptable time step method which maximizes the time step
over a standard Courant-Friedrichs-Lewy condition
\cite[]{Lundbladh1999, AugierChomazBillant2012}.
%
Most of the aliasing is removed by truncating 8/9 of the modes along
each direction \cite[for a detail discussion on the issues of the
non-conservation of the non-quadratic energy and the aliasing errors
in the truncated one-layer shallow water model,
see][]{FargeSadourny1989}.

\subsection{Forced dissipative statistically stationary simulations}

We have carried out a number of simulations 
with large-scale forcing and small-scale dissipation
for different resolutions and different values of the wave speed.
%
The resolution is characterized by the number of nodes in the each
direction, $n$, and has been varied from 240 to 7680.
%
The wave speed $c$ has been varied over two orders of magnitude from
10 to 1000.
%
Table~\ref{tab} presents the parameters for a set of representative
simulations.

\begin{table}
  \begin{center}
% \def~{\hphantom{0}}
\begin{tabular}{cc@{\hskip 8mm}c@{\hskip 8mm}cccc@{\hskip 8mm}cc}
$n$ & $c$ & $\nu_8$ & $\eps$ & $\displaystyle\frac{\kmax}{\kdiss}$ & $\displaystyle\frac{\kdiss}{k_f}$ & $F_f$ & $\min h$ & $\displaystyle\frac{\max |\uu|}{c}$ \\[3mm]
~960 &   10 & 1.5e-10 & 1.03 & 2.46 &  29 &  0.111 & 0.25 & 0.96 \\
1920 &   10 & 9.6e-13 & 1.00 & 2.46 &  58 &  0.110 & 0.37 & 0.92 \\
3840 &   10 & 6.0e-15 & 1.01 & 2.46 & 116 &  0.110 & 0.39 & 1.01 \\
7680 &   10 & 3.7e-17 & 1.03 & 2.46 & 231 &  0.111 & 0.32 & 0.95 \\[1mm]
~960 &   20 & 1.5e-10 & 0.98 & 2.47 &  29 &  0.055 & 0.65 & 0.51 \\
1920 &   20 & 9.6e-13 & 0.84 & 2.48 &  57 &  0.052 & 0.66 & 0.81 \\
3840 &   20 & 6.0e-15 & 0.99 & 2.46 & 115 &  0.055 & 0.56 & 0.68 \\[1mm]
~960 &   40 & 1.5e-10 & 0.99 & 2.46 &  29 &  0.027 & 0.81 & 0.24 \\
1920 &   40 & 9.6e-13 & 1.01 & 2.46 &  58 &  0.028 & 0.78 & 0.28 \\
3840 &   40 & 6.0e-15 & 0.98 & 2.47 & 115 &  0.027 & 0.77 & 0.29 \\
7680 &   40 & 3.7e-17 & 0.94 & 2.47 & 230 &  0.027 & 0.76 & 0.32 \\[1mm]
~960 &  100 & 1.5e-10 & 0.99 & 2.46 &  29 &  0.011 & 0.89 & 0.09 \\
1920 &  100 & 9.6e-13 & 0.98 & 2.47 &  58 &  0.011 & 0.90 & 0.11 \\
3840 &  100 & 6.0e-15 & 0.97 & 2.47 & 115 &  0.011 & 0.87 & 0.13 \\[1mm]
~960 &  200 & 1.5e-10 & 0.99 & 2.46 &  29 &  0.005 & 0.95 & 0.05 \\
1920 &  200 & 9.6e-13 & 0.99 & 2.46 &  58 &  0.005 & 0.94 & 0.06 \\
3840 &  200 & 6.0e-15 & 0.90 & 2.47 & 115 &  0.005 & 0.94 & 0.06 \\[1mm]
~960 &  400 & 1.5e-10 & 0.97 & 2.47 &  29 &  0.003 & 0.97 & 0.03 \\
1920 &  400 & 9.6e-13 & 0.99 & 2.46 &  58 &  0.003 & 0.96 & 0.03 \\[1mm]
~960 & 1000 & 1.5e-10 & 1.16 & 2.45 &  29 &  0.001 & 0.98 & 0.01 \\
1920 & 1000 & 9.6e-13 & 0.91 & 2.47 &  57 &  0.001 & 0.98 & 0.01 \\
\end{tabular}
\caption{Overview of parameters for a set of representative simulations. 
The number of nodes in the each direction is denoted by $n$. 
The size of the numerical domain is equal to $L_h = 50$.
Only the wave numbers $5\delta k\leqslant|\kk|\leqslant8\delta k$ are forced
and the forcing wave number is defined as 
$k_f \equiv 6 \delta k$ 
corresponding to a characteristic forcing scale of approximately 
$L_f \equiv \pi/k_f = 3.57$.
%
$F_f = \eps^{1/3}/({k_f}^{1/3}c)$ is the forcing Froude number and
$\max |\uu|/c$ is the spatial and temporal maximum of a local Froude
number.  }
\label{tab}
\end{center}
\end{table}

The ageostrophic variable $a$ is forced in a shell in spectral space
corresponding to relatively small wave numbers $5\delta k\leqslant
|\kk| \leqslant 8\delta k$, where $\delta k = 2\pi/L_h$.
%
\Add{In the following, we use $L_h = 50$ in order to obtain a
characteristic forcing wave number of order unity, $k_f \equiv 6
\delta k \simeq 0.75$. The corresponding forcing scale is $L_f \equiv
\pi/k_f \simeq 4.2$.}
%
Since only the ageostrophic variable is forced ($\hat f_d = 0$),%
(i) only the thickness fluctuation $\eta$ is forced in the
non-rotating case and %
(ii) the force terms in (\ref{eqapmnum}) are simply equal to $\hat
f_\pm = \hat f_a/2$.
%
In order to compute the force $\hat f_a$, we start from a
pre-normalized force $\hat f_{0}$ obtained from a normal random
process decorrelated in time.
%
The force is then normalized such that the quadratic part of the total
energy $\langle|\uu|^2 + c^2 \eta^2\rangle/2$ is injected at a
constant rate.
%
The spectral injection rate of the quadratic energy averaged over one
time step is (see appendix~\ref{app_comp})
\begin{equation}
P_q(\kk, t) 
= 
\Re\{ \hat \uu(\kk)^* \cdot \hat \ff(\kk) 
+
c^2 \hat \eta(\kk)^* \hat f_\eta(\kk) \}
+ 
(|\hat\ff|^2 + c^2 |\hat f_\eta|^2) \delta t /2,
\end{equation}
where $\Re$ denotes the real part.
%
Writing $\hat f_a = \alpha \hat f_{0}$, it is straightforward to solve
a second-order equation for the coefficient $\alpha$ in order to fix
the injection rate $\Add{P_0 \equiv} \sum_\kk P_q(\kk, t)$ to unity.

The energy is dissipated at the smallest resolved scales by a
hyper-viscous operator, corresponding to a dissipative frequency equal
to $\fdiss(\kk) = \nu_n |\kk|^n$, with $n = 8$.  The value of the
hyperviscosity $\nu_8$ is chosen such as the hyper-Kolmogorov wave
number
\begin{equation}
k_{Kn} = \left( \frac{{\nu_n}^3}{\eps} \right)^\frac{1}{3n-2},
\end{equation}
is well resolved, $\kdiss =k_{K8} \simeq \kmax/ 2.5$, where $\kmax =
(8/9)\pi n/L_h$ is the maximum resolved wave number.

We have observed that when only the waves are forced, the vorticity
does not increase and that when the vorticity is small enough, it does
not significantly influence the waves.  Therefore, we have chosen not
to simulate a negligible vorticity field and to only solve equations
(\ref{eqapmnum}) with $\zeta = 0$.

\begin{figure}
\centerline{\includegraphics[width=13cm]{../Figs/fig_Emean_time}}
\caption{Space averaged energy 
$\langle h|\uu|^2 + c^2 h^2 \rangle/2$ versus time 
for different wave speeds $c$ and resolutions $n$.
%
The energy and the time are normalized by 
$E_f\equiv (P_0/k_f)^{2/3}$ and $T_f\equiv (P_0 {k_f}^2)^{-1/3}$,
with $P_0 = 1 \simeq \eps$.
%
The colors corresponds to different wave speeds as indicated in the figure
$c= 10$, 20, 40, 70, 100, 200, 400, 700 and 1000.
%
The different resolutions are represented by different types of lines:
\Add{thin continuous lines, $n = 240$;
thick dashed lines, $n = 480$;
thin dotted lines, $n = 960$;
thick continuous lines, $n = 1920$;
thin dashed lines, $n = 3840$;
thick dotted lines, $n = 5760$ 
and
thin dotted dashed lines, $n = 7680$.}
}
\label{fig_Evstime}
\end{figure}

The time evolution of the instantaneous total energy is shown in
figure~\ref{fig_Evstime} for different wave speeds $c$.
%
The resolution \Add{and the dissipation wave number are} progressively
increased: %
$n = 240$ ($0\leqslant t/T_f \leqslant 100$), %
$n = 480$ ($100\leqslant t/T_f \leqslant 125$), %
$n = 960$ ($125\leqslant t/T_f \leqslant 140$), %
$n = 1920$, %
$n = 3840$, %
$n = 5760$ and %
$n = 7680$\Add{, where $T_f\equiv
(P_0 {k_f}^2)^{-1/3}$ is the characteristic forcing time}.
%
Each time the resolution is increased, the energy first sharply
increases and then fluctuates.  For most of the simulations, it is
clear that a statistically stationary regime is reached.
%
However, 
%
\Remove{in the relatively short simulations at the highest
resolution for the largest wave speeds ($n = 1920$, $c = 700$ and
1000),}
%
\Add{for some relatively short simulations with very large wave speed
and/or very large resolution,}
%
there are large fluctuations and it is not absolutely certain whether
a statistically stationary regime is reached.
%
\Add{This is in particular the case for the simulations for $c = 700$, $n
= 1920$ (thick red continuous line), $c = 200$, $n = 3840$ (thin
magenta dashed line) and $c=40$, $n = 7680$ (thin blue dotted dashed
line).}
%
\Add{Note that these simulations are already quite numerically
costly. For example, the simulation for $c=1000$ and $n = 1920$
during slightly less than $20T_f$ corresponds to approximately
$8\times 10^5$ time steps.}

Since the energy is injected at large scales and dissipated only at
the smallest resolved scales, the existence of a statistically
stationary regime implies a downscale flux of energy, which is equal
to the large-scale energy injection rate.
%
For the same energy injection rate and resolution, the mean energy
increases with the wave speed, implying that when $c$ increases the
mean energy has to be larger to lead to the same downscale energy
flux.
%
The results presented in the following are from the statistically
stationary regime.  Apart from the snapshots, all shown quantities are
averaged over a period corresponding to this regime.

Table~\ref{tab} presents numerical and physical quantities for a set
of representative simulations.
%
We characterize the simulations by the forcing Froude number
\begin{equation}
F_f \Add{\equiv} \frac{\eps^{1/3}}{{k_f}^{1/3}c}.
\end{equation}
\Add{Since the characteristic forcing wave number and the dissipation
rate are approximately equal to $k_f \equiv 6 \delta k \simeq 0.75$
and $\eps \simeq P_0 = 1$, the forcing Froude number is approximately
inversely proportional to the wave speed: $F_f \simeq 1.1/c$. This
allows us to simply use the wave speed to denote the simulations.}
% where $k_f \equiv 6 \delta k = 0.75$ is a wave number characterizing
% the forcing.
%
The ratio $\kdiss/k_f$ gives an order of magnitude of the width of the
inertial range.  It is a physical quantity related to the numerical
resolution on which the flow can depend.
%
Table~\ref{tab} also displays the minimum thickness $\min(h)$
characterizing the importance of the non-quadraticity of the energy,
and $\max(|\uu|/c)$, which can be interpreted as the maximum of a
local Froude number.

>>>>

We have carried out a series of twenty forced-dissipative simulations of the SW equations in a quadratic domain with periodic boundary conditions using a standard pseudo spectral code. The simulations were started from zero initial conditions and were run till a statistically stationary state was reached. The equations 
were reformulated in terms of  the three eigenmodes of the linearized equations in Fourier space. One of these eigenmodes is zero for an irrotational flow.  
We first carried out a few test simulations in which all three eigenmodes were allowed to evolve in time. However, when only the two wave modes are forced vorticity remains very small throughout the simulations and does not affect the wave dynamics. Therefore, we chose to solve the equations only for the two wave modes. As discussed in the previous section,  a linear viscous term in (\ref{eq_uu}) 
will not conserve momentum exactly and does not give a strictly positive definite expression for energy dissipation. We have relaxed the requirements of exact momentum conservation and positive definite energy dissipation. 
Instead of  using the nonlinear form of the viscous term in (\ref{eq_uu}) we have used a higher order linear operator  $ \nu_8 \nabla^{8} $ both in (\ref{eq_uu}) and
(\ref{eq_h}), where $ \nu_8 $ is a `hyperdiffusion' or a `hyperviscosity'. There is no strong physical motivation for this
modification but, as discussed by \cite{FargeSadourny1989}, a molecular viscous operator 
 of the form $\nu \nabla^2 $ is not necessarily a
relevant model of the actual small-scale dissipation for SW
flows, which should rather be described as a transition from
two-dimensional to three-dimensional motions before reaching the
scales where dissipation actually occurs.
%
Time advancement is carried out by a classical fourth-order
Runge-Kutta scheme for the nonlinear term and an exact integration for
the linear and dissipative terms.  This explicit integration is
especially useful at very high resolution and very large $c$ when
the shortest waves are very fast. 
We use an adaptable time step method which maximizes the time step
over a standard Courant-Friedrichs-Lewy condition
\cite[]{Lundbladh1999, AugierChomazBillant2012}.
%
Most of the aliasing is removed by truncating 8/9 of the modes along
each direction \cite[for a detail discussion on the issues of the
non-conservation of the non-quadratic energy and the aliasing errors
in the truncated one-layer shallow water model,
see][]{FargeSadourny1989}. The resolution is characterized by the number of nodes, $n$, in the each
direction and has been varied from 960 to 7680.
%
The wave speed $c$ has been varied over almost two orders of magnitude from
10 to 700. The wave modes are forced in a shell in spectral space 
corresponding to relatively small wave numbers, 
$ 5 \delta k <  |\kk| <  8 \delta k$,  
where  $ \delta k = 2 \pi /L $ and $ L $ is the length of the side of the quadratic domain. 
The forcing is white noice in time and designed so that the energy injection rate is normalized to unity at each time step.
The energy is dissipated at the smallest resolved scales by hyperviscosity.
The value of the
hyperviscosity, $\nu_8$, is chosen in such a way that the  maximum wave number is larger than the dissipation wave number
\begin{equation} 
k_{d} = \left( \frac{{\nu_8}^3}{\eps} \right)^{-\frac{1}{22}},
\end{equation}
 where $ \eps $ is the mean energy dissipation rate. We found that  $
 k_{d} \simeq \kmax/ 2.5$, where $\kmax =
(8/9)\pi n/L $ is the maximum wave number, is  sufficient in order for dissipation spectra to be resolved. Since the energy injection rate is normalized to unity and all simulations reach a stationary state in which dissipation is equal to the injection rate, $ \nu_8 $ can be chosen already from the start so that this condition will be fulfilled in the stationary state.  The strength of the stratification is characterized by a Froude number, defined as
\begin{equation} \label{Fr}
F_f = \frac{\varepsilon^{1/3}}{c k_f^{1/3}} \, ,
\end{equation} 
a parameter that can be determined from the start of each simulations. 
The  simulation parameters are listed in table 1.

\begin{table}
\begin{center}

\label{Table1}
\begin{tabular}{lrrrrrrrr}

\toprule
{} &   $n$ &  $c$ &  $\nu_8$ &  $\eps$ &  $ k_{d}  / {k_f} $ &   $F_f$ &    $t_{\max}$ \\
\midrule
W1  &   960 &   10 & 1.56e-10 &        1.04 &                    28.8 &   0.111 &                49.9 \\
W2  &  1920 &   10 & 9.68e-13 &        1.06 &                    57.7 &   0.112 &               49.8 \\
W3  &  3840 &   10 &    6e-15 &         1.10&                     115 &   0.113 &               49.9 \\
W4  &  7680 &   10 & 3.72e-17 &        1.18 &                     231 &   0.116 &               49.9 \\
W5  &   960 &   20 & 1.56e-10 &           1.00 &                    28.8 &   0.055 &              49.9 \\
W6  &  1920 &   20 & 9.69e-13 &        1.02 &                    57.7 &  0.0553 &                120 \\
W7  &  3840 &   20 & 6.01e-15 &        1.08 &                     115 &  0.0563 &                120 \\
W8  &  7680 &   20 & 3.72e-17 &        1.21 &                     231 &  0.0585 &                 120 \\
W9  &   960 &   40 & 1.56e-10 &          1.00 &                    28.8 &  0.0274 &                49.8 \\
W10 &  1920 &   40 & 9.68e-13 &       1.00 &                    57.7 &  0.0274 &               49.8 \\
W11 &  3840 &   40 &    6e-15 &        1.06 &                     115 &   0.028 &               49.8 \\
W12 &   960 &  100 & 1.56e-10 &       1.00 &                    28.8 &   0.011 &                49.8 \\
W13 &  1920 &  100 & 9.69e-13 &        1.01 &                    57.7 &   0.011 &                 120 \\
W14 &  3840 &  100 & 6.01e-15 &        1.06 &                     115 &  0.0112 &                 120 \\
W15 &  7680 &  100 & 3.72e-17 &        1.22 &                     231 &  0.0117 &                95.8 \\
W16 &   960 &  400 & 1.56e-10 &        1.14 &                    28.8 & 0.00287 &                 120 \\
W17 &  1920 &  400 & 9.69e-13 &        1.15 &                    57.7 & 0.00288 &                 120 \\
W18 &  3840 &  400 & 6.01e-15 &        1.12 &                     115 & 0.00286 &                119 \\
W19 &   960 &  700 & 1.56e-10 &        1.27 &                    28.8 &  0.0017 &                49.8 \\
W20 &  1920 &  700 & 9.68e-13 &        1.05 &                    57.7 &  0.0016 &                49.8 \\
\bottomrule

\end{tabular}
\caption{Parameters for all simulations. $ n $: number of nodes in each direction, $ c $: wave speed, $ \nu_8 $: hyperviscosity, $ \eps $: time averaged mean energy dissipation in the stationary state, $ k_{d}/ k_f $: ratio between dissipation wave number and forcing wave number, $ F_f  $: Froude number, $ t_{max} $:   end time of simulation.}
\end{center}
\end{table}

\begin{figure}
\centerline{\includegraphics[width=5.12in]{../Pyfig/fig_Emean_time}}
\caption{Space averaged energy, 
$E = E_K + E_A $, versus time 
for all simulations. }
\label{fig_Evstime}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=5.8in]{../Pyfig/fig_energy_w}}
\caption{Left: Mean energy in the stationary state versus $ c $ for different resolutions. The lines have slope $ 0.5 $, corresponding to $ E \propto c^{1/2} $. Right: Normalized mean energy in the stationary state versus resolution $ n $ for different $ c $.}
\label{MeanE}
\end{figure}

The time evolution of  
mean energy is shown in
figure~\ref{fig_Evstime} for all twenty simulations. After an initial period of growth, mean energy is leveling out at different values for different runs.  This is not the same picture as we see in simulations of three-dimensional incompressible turbulence or stratified turbulence, where all curves would have leveled out more or less at the same value. We find that mean energy in the stationary state is a function of both $ c $ (or the Froude number) and resolution $ n $ and that the functional dependence  can be approximately written as
\begin{equation} \label{MeanEnergy}
E \propto \sqrt{L_f c \eps} \, n^{\alpha}  \, ,
\end{equation} 
where $ L_f = \pi/k_f $ is the forcing scale. In figure \ref{MeanE} to the left, we see $ E/\sqrt{\eps} $ as function of $ c $ for different resolutions $ n $. For each resolution the  points are approaching a power law $ C_n c^{1/2} $  with increasing values of $ C_n $ for increasing $ n $. In the same figure to the right we see 
$ E/\sqrt{L_f c \eps} $ for different values of $ c $. For each $ c $ the points follow a power law $ n^{\alpha} $, where $ \alpha $ is becoming slightly larger with increasing $ c $, approaching almost the same value $ \alpha \approx 0.33 $ for the three highest values of $ c $.  The relation (\ref{MeanEnergy}) can be reformulated as
\begin{equation} \label{Dissipation}
\frac{\eps} {(E^{3/2} / L_f)} \propto \frac{E^{1/2}}{c} n^{-2\alpha}
\end{equation} 
Since the simulations are well resolved the dependence on resolution should not be interpreted as consequence of the numerics but rather as a Reynolds number effect, although it is not hundred percent clear how a Reynolds number should be defined in our case.  We may note, however, that $ n $ is  proportional $ k_{d} / k_f $ and  the corresponding ratio in Kolmogorov turbulence scales as $ Re^{3/4} $ since the Kolmogorov scale is proportional to $ \nu^{3/4} $, where $ \nu $ is the kinematic viscosity. If we simply define a Reynolds number as
\begin{equation}
Re = \left ( \frac{k_d} {k_f} \right )^{4/3} \, ,
\end{equation} 
we can substitute $ n^{-2\alpha} $ in (\ref{Dissipation}) with $ Re^{-8 \alpha/3} $.  The normalised energy dissipation on the left hand side of  (\ref{Dissipation}) will thus go to zero in the limit of large Reynolds number. This is very different from three-dimensional turbulence 
where there is a local Richardson-Kolmogorov cascade, in which energy is successively transfered from large to small scales of motion.  That the cascade is local means that eddies of a particular scale are not directly influenced by eddies of widely different scales. As a consequence, the normalized dissipation is of the order of unity independent of Reynolds number \cite[]{Pope, TennekesLumley}. A review of the experimental evidence and theoretical implications of this fundamental law of Kolmogorov turbulence is given by \cite{Vassilicos2015}. 
Our result (\ref{Dissipation})  suggests that SW wave turbulence does not fit into the paradigm of a local Richardson-Kolmogorov cascade. Moreover, it is not only in the limit of large Reynolds number the normalized dissipation will go to zero but also in the limit of strong stratification, $ E^{1/2}/c \rightarrow 0 $. This is  different from three-dimensional stratified turbulence where the ratio on the left hand side of (\ref{Dissipation}) is of the order of unity in the limit of strong stratification  \cite[]{Lindborg2006, Brethouwer2007}.

 The `four-fifths law' for the third order structure function of Kolmogorov turbulence is often derived using the assumption of a local cascade \cite[]{Vassilicos2015} or the assumption that dissipation stays finite in the limit of large Reynolds number \cite[]{Frisch}. As we just discussed, these assumptions seem to be violated in the case of SW wave turbulence. Nevertheless, the analogous law (\ref{eq_Kolmo}) that we derived for SW wave turbulence is satisfied with a high degree of accuracy in our simulations. In figure \ref{Flux} we wee the spectral energy flux from run W7 to the left and the third order structure function to the right. There is a broad constant flux range  with equipartition between KE and APE flux and an almost equally broad range where (\ref{eq_Kolmo}) is satisfied, with equipartition between the two third order structure functions associated with KE and APE. The assumptions of a local cascade and finite dissipation do not seem to be necessary in order for the third order structure function law  (\ref{eq_Kolmo}) to be valid.

\begin{figure}
\centerline{\includegraphics[width=5.8in]{../Pyfig/fig_flux_struct_combined}}
\caption{Left: Time averaged normalised spectral energy fluxes versus $ k/k_f $. Right: Time averaged normalised third order structure functions versus $ r/L_f $. From run W7. }
\label{Flux}
\end{figure}

\begin{figure}
 \centerline{
 \includegraphics[width=3.15in]{../Pyfig/fig_spatiotempspectra}}
\caption{Frequency spectra of KE  and APE for different $ k = \mid {\bf k} \mid $, from run W7. The spectra are plotted  as functions of $\omega/\omega_l$, where
$\omega_l = c k$.  From top to bottom: $ k /\delta k
= 12$, 27, 62, 143, 327, and 746.  }
\label{fig_spatiotemp_spectra}
\end{figure}
\begin{figure}
 \centerline{
 \includegraphics[width=6.0in]{../Pyfig/fig_phys_fields_wave}}
\caption{Left: divergence $ \bnabla \cdot {\bf u} $. Right: velocity component in the $ y $-direction: $ u_y $. Top: run W6. Bottom: run W17.  }
\label{Physical}
\end{figure}
\begin{figure}
\centerline{\includegraphics[width=8cm]{../Pyfig/fig_shock_sep.pdf}}
\caption{Mean distance between the shocks as function of Froude number.  }
\label{fig_distance}
\end{figure}

The equipartition of KE and APE spectral fluxes suggests that the flow to leading order may be described as a collection of linear gravity waves with equipartition of KE and APE in each mode. To investigate this further we have collected time series of the flow variables from Fourier modes whose magnitude fall within certain shells,  $ \mid {\bf k} \mid \in [ k -\delta k/2, \; k+ \delta k/2] $,  and computed temporal power law spectra from these time series and averaged over all wave numbers in each shell.  In other words we have computed KE and APE frequency spectra corresponding to different magnitudes of modes. 
Figure~\ref{fig_spatiotemp_spectra} presents such
spectra plotted as a functions of the normalized frequency
$\omega/\omega_l$, where $ \omega_l = kc $ is the linear wave frequency, 
The spectra are strongly dominated by  peaks at $\omega =
\omega_l$. As can be seen, there is equipartition between KE and APE in each shell.  
Although the widening of the peaks around the linear frequency most likely is an effects of nonlinearities, 
we can quite safely conclude that the time evolution of the flow variables in each Fourier mode to leading order can be described as a linear wave.

Visualizations of the flow field give a completely different picture from what may be expected from a collection of linear gravity waves. They are totally dominated by the appearance of shock waves. In figure (\ref{Physical}) we see the divergence, $ \nabla \cdot {\bf u} $, to the left and the velocity component in the $ y $-direction, $ u_y $, to the right. The two figures at the top are from run W6 while the two figures at the bottom are from run W17. The difference between the two runs is that $ c $ is larger by a factor of $ 20 $ in W17 as compared to W6. To the left we see the shocks displayed as elongated bands of negative divergence. That the divergence is negative at the shocks can be understood from the fact that the velocity component perpendicular to the shock always has a negative jump in the direction of shock propagation. Apparently, the mean distance between the shocks is considerably smaller in run W17 with the larger value of $ c $ compared to run $ W6 $  with the smaller value of $ c $. The shocks are also visible in the figures to right where $ u_y $ is displayed. It may be interesting to note that the shocks along the $ x $-axis appear as extra sharp in this plot, since there is a strong jump  of $ u_{y} $ over these shocks, while the shocks along the $ y $-axis are hardly visible, since there is no jump of $ u_{y} $ over these.  In the two figures to the right we see a variation of the flow field over the length scale $ L_f $ which is not seen in the two figures to the left. This variation is evidently a footprint of the random forcing. 
Although the forcing length scale $ L_f $ is the same in the two simulations the mean distance, $ d $,  between the shocks is much smaller in run $ W17 $ than in run $ W6 $, which may seem a little bit surprising. We have calculated $ d $ by counting the number of negative spikes of the divergence along ten lines parallel to the $ x $-axis and ten lines parallel to the $ y $-axis and then divided  total length of all the lines by the number of spikes. Generally, we found that $ d \sim c^{-1/2} $, or
\begin{equation} \label{MeanDistance}
d \propto L_f F_f ^{1/2} \, ,
\end{equation} 
independent of resolution $ n $.
In figure (\ref{fig_distance}) we have plotted $ d/L_f $ versus Froude number for all twenty runs. As can be seen the points follow the $ F_f^{1/2} $-curve quite well, although there seems to be a slight systematic deviation at the highest $ F_f $, which may be due to the fact that $ d $ is rather close to the length of the side of the box for the largest $ F_f $.

\begin{figure}
 \centerline{
 \includegraphics[width=5.0in]{../Pyfig/fig_struct_order_246}}
\caption{From top to bottom: second, fourth and sixth order compensated and normalised longitudinal structure functions. Left: runs with $ n=3840 $: W3, W7, W11 and W18. Right: runs with $ n = 7860 $: W4, W8 and W15. }
\label{fig_StrucFunc}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=8cm]{../Pyfig/fig_ratio_strfct}}
\caption{
Ratio of the structure functions 
$R_p(r) = \mean{|\delta u_L|^p} / \mean{|\delta u_T|^p}$ from run W4, 
for $ p = 2, \, 3, \, 4, \, 5, \, 6. $
The dotted straight lines indicate the values predicted by (\ref{Ratio}):
$R_2 = 2$, $R_3 = 3\pi/4$,  $R_4 = 8/3$, $ R_5 = 15 \pi /16 $ and $ R_6 = 16/5 $.}
\label{fig_ratio}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=12cm]{../Pyfig/fig_flatness}}
\caption{ Flatness of the longitudinal and transverse increments for
$c = 10$ and $n = 7680$. The straight continuous lines indicate the
$r^{-1}$-scaling and the straight dashed line the $r^{-3/2}$-scaling.
The inset shows the ratio $F_T/F_L$ and the corresponding value computed by the shock model, $F_T/F_L = 1.5$.  }
\label{fig_flatness}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=11cm]{../Pyfig/fig_spectra}}
\caption{Compensated and normalised energy spectra
from runs with $ n = 7680 $: W4, W8 and W15.}
\label{fig_spectra_c40}
\end{figure}

We will now present the results for the structure functions. Substituting (\ref{MeanDistance}) into (\ref{StrucFunc}) we find that the structure functions are expected to scale as
\begin{equation} \label{StrucFunc2}
\meane{|\delta u |^p}  \sim \meane{(c|\delta h |)^p} \sim  (L_f F_f^{1/2})^{p/3-1}  \eps^{p/3}  r  \, .
\end{equation}
for separation distances that fulfill the condition $ \delta x \ll r \ll d $, where $ \delta x $ is the shock width. The scaling (\ref{StrucFunc2}) is expected to become better and better fulfilled with decreasing $ c $ (or increasing $ F_f $), for two reasons. 
First, according to (\ref{MeanDistance}) $ d $ is increasing with $ F_f $, and the scaling range is therefore becoming wider for decreasing $ c $, if  $ \delta x $ or the resolution  $ n $ is kept constant. Second, according to (\ref{Strength}) the amplitude of the shocks scales as $ (\eps d)^{1/3} $, which means that the shocks are becoming increasingly strong for large $ d $ (small $ c $). Thus, the assumption that the structure functions are totally dominated by increments where a shock is crossed will be better fulfilled for small $ c $. This effect is expected to be particularly important for lower order structure functions. The scaling (\ref{StrucFunc2}) is also expected top become better and better fulfilled with increased resolution $ n $, since $ \delta x $ is decreasing with increasing $ n $.

 As expected, we have found that 
the displacement structure functions scale exactly in the same way as the velocity structure functions, why we only plot velocity structure functions. In figure (\ref{fig_StrucFunc}) we see the compensated and normalised second, fourth and sixth order longitudinal structure functions from the five simulations with $ n = 3840 $ to the left and the three simulations with $ n = 7860 $ to the right. At small separation, $ r < \delta x $, the structure functions have the dependence $ \sim r^{p} $, which is characteristic of a smooth velocity field, indicating that the shocks are reasonably well resolved. There is a small bump around the shock width, 
$ r \approx \delta x $, and at $ r > \delta x $, there is a range where the compensated structure functions are flat, or almost flat. As expected, this range is becoming broader for smaller  $ c $ (or larger $ F_f $). The range is also broader in the higher resolution runs to the right as compared to the lower resolution simulations to the left.  There is clearly a better collapse of the curves for the sixth order structure functions compared to the second order structure functions. This is not surprising, since the shock contribution to the structure functions should become increasingly dominant with increasing order. Plots of the transverse structure functions are very similar to the plots of the longitudinal structure functions, with the difference that the transverse structure functions are somewhat smoother at $ r \approx \delta x $. In figure (\ref{fig_ratio}) we see the ratio $ R_{p}(r) = \langle \mid \delta u_L \mid ^{p} \rangle /  \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p= 2,3,4,5,6 $ from run W4, together with dotted straight lines, indicating the values predicted by (\ref{Ratio}). As can be seen, there is a quite good agreement with the predicted values in a limited range of separations, $ r > \delta x $. Somewhat unexpectedly, the range in which there is a good agreement becomes more narrow with increasing $ p $, an observation that we cannot explain. It may also be noted that $ R_2 \rightarrow 3 $ in the limit of small $ r $, which is the theoretical single point limit for an irrotational isotropic field. In figure (\ref{fig_flatness}) we se the flatness factor, $ F_T $,  of the transverse structure functions at the top and the ratio, $ F_T/F_L $,  at the bottom. The figures to the left show the results from the five simulations with  $ n = 3840 $ and the figures to the right show the results from the three simulations with $ n = 7860 $. The flatness factor  shows increasingly large values for decreasing $ r $ with a dependence that is rather close to but somewhat steeper than $ r^{-1} $. At small $ r $ the curves  are leveling out at very large values. For $ n = 7869 $ and $ c = 10 $ we see that $ F_{T} \approx 400 $ at small $ r $. 
The degree to which the flatness factor is increasing with decreasing scale is by some authors defined  as the most appropriate measure of spatial intermittency \cite[see for example][]{Frisch}. If this measure is used, SW wave turbulence is, indeed, extremely intermittent.  In the two figures at the bottom we see that $ F_{T}/F_{L} \approx 1.5 $ in a limited range of separations, $ r > \delta x $, which is becoming somewhat broader as $ c $ is increasing and  is also somewhat broader in the higher resolution runs shown to the right as compared to the lower resolution runs shown to the left. This is in accordance with the shock model predictions (\ref{FL}) and (\ref{FT}).
